MSDS6372 - Final Project

### 2018-03-31 MSDS6372_Final_Project_BBHOF.Rmd
Added ROC plot and AUC calculation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# required libraries
library(kableExtra) # to make uber sexy tables for output
library(pastecs) # for easy descriptive statistics
library(ggbiplot) # implementation of biplot using ggplot2 for plotting PCs
library(Amelia) # cool library for exploring missing data

@@

```{r, echo=TRUE, fig.width=8, fig.height=10}
# display missing values
missmap(BBHOFRaw, main="Missing Values in Raw Data")

@@

```{r, echo=TRUE}
# display frequency table for did/did not get inducted into HOF
# since the labels also include 2, converting those to 1, so the result is truly binary (1, 0)
BBHOFRaw$HOFMembership[BBHOFRaw$HOFMembership == 2] <- 1
count(BBHOFRaw, "HOFMembership")

@@

# calculate the mean of the fitted results that don't equal the observed result - IGNORE NAs
misClasificError <- mean(fittedresults != test$HOFMembership, na.rm=TRUE)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# required libraries
library(kableExtra) # to make uber sexy tables for output
library(pastecs) # for easy descriptive statistics
library(ggbiplot) # implementation of biplot using ggplot2 for plotting PCs
library(Amelia) # cool library for exploring missing data
library(ROCR) # for ROC plots and AUC calculations

@@

```{r, echo=TRUE, fig.width=8, fig.height=10}
# display missing values map (graphic)
missmap(BBHOFRaw, main="Missing Values in Raw Data")

# display number of NAs
sapply(BBHOFRaw, function(x) sum(is.na(x)))

@@

```{r, echo=TRUE}
# display frequency table for did/did not get inducted into HOF
BBHOFRaw$HOFMembership[BBHOFRaw$HOFMembership == 2] <- 1# since the labels also include 2, converting those to 1, so the result is truly binary (1, 0)
BBHOFRaw$HOFMembership[BBHOFRaw$HOFMembership == 2] <- 1
count(BBHOFRaw, "HOFMembership")

@@

# calculate the mean of the fitted results that don't equal the observed result - IGNORE NAs
misClasificError <- mean(fittedresults != test$HOFMembership, na.rm=TRUE) # this adds up all the instances of misclassification then divides by total (via mean)

@@

and now some ROC curves...

pr <- prediction(fittedresults, test$HOFMembership)
prf <- performance(pr, measure = "tpr", x.measure = "fpr")
plot(prf)

auc <- performance(pr, measure = "auc")
auc <- auc@y.values[[1]]
auc
